---
name: Griffin
surname: Going
position: "Student"
address: "4472 Bonanza Dr NE - Grand Rapids, MI"
phone: +1 (616) 516-4145
profilepic: images/GriffinGoing.jpg
www: 
email: "GriffinGoing@gmail.com"
github: GriffinGoing
linkedin: GriffinGoing
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "While studying music as a college undergraduate, I took an introductory computer programming course which opened me up to a whole new world. A strong self starter, I dove in and began pursuing computer science as a full-time career. I love the ongoing challenge to learn that a career in CS demands, and I am eager to continue my journey. "
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "A.M. in Piano Performance", "2014-2017", "Grand Rapids Community College", "Grand Rapids, Michigan",
  "B.S. in Computer Science", "2018-2021", "Grand Valley State University", "Allendale, Michigan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Projects

## NaviGatr In-Building Mapping Application 

 * Designed and created (with a team) an app for navigating inside buildings via Dijkstra's Algorithm
 * Enabled easy navigation between rooms with visual and written directions 
 * Companion app enabled the creation of maps over any image or floor plan
 
## Conversion of Music to Haptic Vibrations on a Worn Device 
 * Working to compress wave frequency up to 20,000 Hz to a 500 Hz range 
 * New waves sent in haptic form to a wearable device 
 * This method allows those with hearing loss experience music in a new way 

# Languages

```{r language-experience, fig.align='left', fig.width=5.25, fig.height=3.5}
# Scale - some exp, exp, lots of exp 
level_descriptors <- tribble(
  ~ Level, ~ Experience,
  1, "A Little Experience",
  2, "Moderate Experience",
  3, "Significant Experience"
)

# The 'ol inpsired join
tribble(
  ~ Language, ~ Level,
  "R", 2,
  "NodeJS", 1,
  "Python", 3,
  "Java", 3,
  "C", 2,
  "SQL", 1,
  "C++", 2
) %>%
  left_join(level_descriptors, by = "Level") %>%
  ggplot(mapping = aes(x = Language, y = Experience, fill = Language)) +
  geom_col() +
  theme_minimal() +
  labs(
    x = "",
    y = "",
    caption = ""
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
    )
```

# Design Principles and Libraries

## React

- Built a location-based weather service **React** app using the **Bootstrap** library
- Primarily used collaborative information from the *National Weather Service* API

## REST API

- Built a front-end client for searching the International Games Database
- Functionality includes: searching the database, selecting a search result, and navigating available selection information
- Client automatically re-queries the API if redirect information is returned

```{R para}
#stuff like React and whatnot, leaving for parameterization down the road
```

# Work Experience

Bonefish Grill, Grand Rapids, MI — Inventory Manager • *February 2016 - August 2020*

 - Oversaw the successful implementation of a new digital payment system
 - Optimized inventory tracking/ordering process to save both time and money 
 - Modified computer workflow assets/processes to increase productivity 
  
&nbsp;

## *References available upon Request*

*This resume is kept updated on github [here](https://github.com/GriffinGoing/Griffin-Going-Resume/blob/master/GriffinGoingResume.pdf).*

# Awards

```{r, eval=FALSE}
# keeping in the template in case I win anything *shrugs*
tribble(
  ~Year, ~Type, ~Desc,
  2019, "Mathematics", "SIMIODE",
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


```{r, eval=FALSE}
# keeping in case I write anything like, 10-20 years from now
library(dplyr)
scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("curie.bib")

bibliography_entries("curie.bib")
```

