---
name: Griffin
surname: Going
position: "Student"
address: "Grand Rapids, MI"
phone: +1 (616) 516-4145
profilepic: images/GriffinGoing.jpg
www: Coming Soon!
email: "GriffinGoing@gmail.com"
github: GriffinGoing
linkedin: GriffinGoing
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "While studying music as a college undergraduate, I took an introductory computer programming course which opened me up to a whole new world. A strong self starter, I dove in and began pursuing computer science as a full-time career. I love the ongoing challenge to learn that a career in CS demands, and I am eager to continue my journey. "
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "A.M. in Piano Performance", "2014-2017", "Grand Rapids Community College", "Grand Rapids, Michigan",
  "B.S. in Computer Science  -  GPA: 3.67", "2018-2021", "Grand Valley State University", "Allendale, Michigan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Projects

## In-Building Mapping/Navigation Application 

 * Designed and created (with a team) an app for navigating inside buildings via Dijkstra's Algorithm
 * Enabled easy navigation between rooms with visual and written directions 
 * Companion app enabled the creation of maps over any image or floor plan
 
## Conversion of Music to Haptic Vibrations on a Worn Device 
 * Working to compress wave frequency up to 20,000 Hz to a 500 Hz range 
 * New waves sent in haptic form to a wearable device 
 * This method allows those with hearing loss experience music in a new way 
 
## Mel Frequency Cepstrum Coefficients Dashboard
 * Built an online dashboard for extracting and analyzing MFCC features from .wav files
 * Offers interactive plot manipulation and visualization options
 * Allows users to see extracted features relevant to audio training algorithms in direct juxtaposition


# Languages

```{r language-experience, fig.align='left', fig.width=5.25, fig.height=2.75}
# Scale - some exp, exp, lots of exp 
level_descriptors <- tribble(
  ~ Level, ~ Experience,
  1, "A Little Experience",
  2, "Moderate Experience",
  3, "Significant Experience"
)

# The 'ol inpsired join
tribble(
  ~ Language, ~ Level,
  "R", 2,
  "NodeJS", 1,
  "Python", 3,
  "Java", 3,
  "C", 2,
  #"SQL", 1,
  "C++", 2
) %>%
  left_join(level_descriptors, by = "Level") %>%
  ggplot(mapping = aes(x = Language, y = Experience, fill = Language)) +
  geom_col() +
  theme_minimal() +
  labs(
    x = "",
    y = "",
    caption = ""
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
    )
```

# Design Principles and Libraries

* **React**
* **Bootstrap / JSX**
* **REST API**

```{R para}
#stuff like React and whatnot, leaving for parameterization down the road
```

# Work Experience

Applied Computing Institute — Software Developer • *September 2020 - Current*

 - Performing research on the application of MFCC techniques to specific audio-classifying ML algorithms
 - Working on a small team to develop an audio analysis software suite

Bonefish Grill — Inventory Manager • *February 2016 - August 2020*

&nbsp;

## *References available upon Request*

*This resume is kept updated on github [here](https://raw.githubusercontent.com/GriffinGoing/Griffin-Going-Resume/master/GriffinGoingResume.pdf).* *

* *Due to its parameterized format, this resume is updated automatically. If hyperlinks are unavailable in the current PDF viewer due to deprecation, please don't hesitate to visit my Github page for a current version of this resume, or to reach out with any questions. I welcome inquiry into my current passion projects and the research therein.*


```{r, eval=FALSE}
# Awards

# keeping in the template in case I win anything *shrugs*
tribble(
  ~Year, ~Type, ~Desc,
  2019, "Mathematics", "SIMIODE",
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


```{r, eval=FALSE}
# keeping in case I write anything like, 10-20 years from now
library(dplyr)
scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("curie.bib")

bibliography_entries("curie.bib")
```

