---
name: Griffin
surname: Going
position: "Software Developer"
address: "Grand Rapids, MI"
phone: +1 (616) 516-4145
profilepic: images/GriffinGoing.jpg
www: Coming Soon!
email: "GriffinGoing@gmail.com"
github: GriffinGoing
linkedin: GriffinGoing
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "While studying music as a college undergraduate, I took an introductory computer programming course and was immeditaely captivated. A strong self starter, I dove in and began pursuing computer science as a full-time career. I love the ongoing challenge to learn that a career in CS demands, and I am eager to continue my journey. "
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "B.S. in Computer Science  -  GPA: 3.7", "2018-2021", "Grand Valley State University", "Allendale, Michigan",
  "A.M. in Piano Performance", "2014-2017", "Grand Rapids Community College", "Grand Rapids, Michigan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Projects

## Easy Engine - Python Game Engine

 * Extends the `pygame` library to provide easy access to features commonly required by games
 * Requires minimal input from the user, and formats input to spec internally
 * Uses verbose in-process benchmarking for accurate timing across machines and environments.
 
## Conversion of Music to Haptic Vibrations on a Worn Device 
 * Working to compress wave frequency up to 20,000 Hz to a 500 Hz range 
 * New waves sent in haptic form to a wearable device 
 * Allows those with hearing loss experience music in a new way based on research contrasting neural touch receptor and auditory sensor responses.
 
## Mel Frequency Cepstrum Coefficients Dashboard
 * Built an online dashboard for extracting and analyzing MFCC features from .wav files
 * Offers interactive plot manipulation and visualization options
 * Allows users to see extracted features relevant to audio training algorithms in direct juxtaposition, or by individual datasets.


# Languages

```{r language-experience, fig.align='left', fig.width=5.25, fig.height=1.5}
# Scale - some exp, exp, lots of exp 
level_descriptors <- tribble(
  ~ Level, ~ Experience,
  1, "A Little Experience",
  2, "Moderate Experience",
  3, "Significant Experience"
)

# The 'ol inspired join
tribble(
  ~ Language, ~ Level,
  "R", 3,
  "NodeJS", 2,
  "Python", 3,
  "Java", 3,
  "C", 2,
  #"SQL", 1,
  "C++", 1
) %>%
  mutate(
    Language = factor(Language, levels=c("C++", "C", "NodeJS", "Java", "Python", "R"))
  ) %>%
  left_join(level_descriptors, by = "Level") %>%
  ggplot(mapping = aes(x = Language, y = Experience, fill = Language)) +
  geom_col() +
  theme_minimal() +
  labs(
    x = "",
    y = "",
    caption = ""
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
    )
```

```{R para}
#stuff like React and whatnot, leaving for parameterization down the road
```

# Work Experience

Applied Computing Institute — Software Developer • *August 2020 - Current*

 - Performing research on the application of MFCC audio feature extraction techniques to specific audio-classifying ML algorithms. Example questions include: how much water is being used within a given audio clip based on the sounds of the running water? If someone is brushing their teeth, which region of their mouth are they brushing, and by what metrics can MFCCs confirm this?
 - Developing mobile solutions for data collection and classification via React and Core ML. These solutions are meant to be attractive and easy-to-use for all users, increasing both the accuracy of the data, and the amount gathered.
 - Building browser-based solutions via React with an emphasis on end-user ease-of-use and clearly defined classification of qualitative data.
 - Implementing these models in mobile applications (via Swift) designed to give users feedback on such nuances as oral hygiene, excess water use, and more. 

Bonefish Grill — Inventory Manager • *February 2016 - August 2020*

## *References available upon Request*

*This resume is kept updated on github [here](https://raw.githubusercontent.com/GriffinGoing/Griffin-Going-Resume/master/GriffinGoingResume.pdf).* *

* *Due to its parameterized format, this resume is updated automatically. If hyperlinks are unavailable in the current PDF viewer due to deprecation, please don't hesitate to visit my Github page for a current version of this resume, or to reach out with any questions. I welcome inquiry into my current passion projects and the research therein.*


```{r, eval=FALSE}
# Awards

# keeping in the template in case I win anything *shrugs*
tribble(
  ~Year, ~Type, ~Desc,
  2019, "Mathematics", "SIMIODE",
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


```{r, eval=FALSE}
# keeping in case I write anything that gets published
library(dplyr)
scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("curie.bib")

bibliography_entries("curie.bib")
```

